\documentclass{manual}


\author{Sean Ross-Ross }

\title{SLIMpy Refrence Guide}

\makeindex

\authoraddress{
        Seismic Laboratory for Imaging and Modeling  \\
        Email: \email{srossross@google.com}
}

\begin{document}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\ifhtml
\chapter*{Front Matter\label{front}}
\fi

\include{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\include{license}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{ Introduction }

\begin{notice} [note] 
This is not a complete refrence to SLIMpy. For the complete dsocumentation see the
\citetitle[../../auto/SLIMpy.html]{SLIMpy Pydoc}
\end{notice}

\chapter{Command Line Options}
	
\begin{tableiii}{l|l|l}{programopt}{Short Options}{Long
Options}{Description}

  \lineiii{-h} {\longprogramopt{help}}
              {show a help message and exit}
              
  \lineiii{-v} {\longprogramopt{verbose}=1}
                        {print various outputs to stderr 0 to 10}
                        
  \lineiii{-m} {\longprogramopt{memsize}=500}
                        {memory size to pass to out-of-core functions in MB}
                        
  \lineiii{-q}{\longprogramopt{quiet}} 
  				           {print no output to stderr}
  				           
  \lineiii{-t} {\longprogramopt{tmpdir}=TMPDIR}
                        {Temporary directory to store header information}
                        
  \lineiii{-p}{\longprogramopt{pipe}} 
  			            {Use the bilt-in pipe structure of (p)SLIMpy -efficient for
  			            out-of-core use}
  			            
  \lineiii{-i}{\longprogramopt{no-pipe}}         
  						{Do not use the
  						bilt-in pipe structure of (p)SLIMpy -Good for debugging }
  						
  \lineiii{ }{\longprogramopt{tmpdatapath}=TDP}
  					    { Directory to store temporary binary data }
  \lineiii{ }{\longprogramopt{globaltmpdir}=GTD}
  						{Global temporary directory.  Used in parallel computation to share data.}
  \lineiii{ }{\longprogramopt{localtmpdir}=LTD}
  					    { Local temporary directory.  Used in parallel computation to work
  					    locally.}
  \lineiii{ }{\longprogramopt{eps}=EPS} 
  				       {Parallel only. Domain decomposition overlap parameter.
                        Common across all dimensions.}
  \lineiii{ }{\longprogramopt{nwin}=NWIN}
  						{Parallel only. Defines domain decomposition across all
                         dimensions. }
  \lineiii{-s}{\longprogramopt{scons}}
  						{output a scons file to stdout}
  \lineiii{-d}{\longprogramopt{dot}}
  						{output a dot file to stdout}
  \lineiii{-n}{\longprogramopt{dryrun}}
  						{print output only do not run commands}
  \lineiii{-l}{\longprogramopt{log}=FILE}
  						{file to write all output to}
  \lineiii{ }{\longprogramopt{debug}=DEBUG}         
  						{print output only relative to crertain debug types:
                         cleaner display solver}
  \lineiii{ }{\longprogramopt{test}}
  		                 {run a test suit to test the slimpy framework}
	
\end{tableiii}

\begin{definitions} 

\term{help}

\term{verbose}
	
\term{memsize}
\term{quiet}
\term{tmpdir}
\term{pipe}
\term{no-pipe}      
\term{tmpdatapath}
\term{globaltmpdir}
\term{localtmpdir}
\term{eps}
\term{nwin}
\term{scons}
\term{dot}
\term{dryrun}
\term{log}
\term{debug}
\term{test}
  
  
\end{definitions}

\chapter{ Packages }

\refmodule [Vector]{Vector}

\include{Vector}

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%